\documentclass{beamer}

\usepackage{lmodern}
\usepackage{attrib}
\usepackage{verse}
\usepackage{altverse}
\usepackage{bibleref}

\title{Physicians are for the Sick}
\subtitle{The Life Of Jesus}
%\author[WSCOC]{Walnut Street Church of Christ}
\date{March 02, 2014}

\AtBeginSection[]
{
\begin{frame}
\frametitle{Physicians are for the Sick}
\tableofcontents[currentsection]
\end{frame}
}

\begin{document}
\frame{\titlepage}

\begin{frame}
\frametitle{What are you really saying when...}

you are a snob,

you whine about things at church,

you can't handle the horrific nature of your brother's sin,

you are more merciful to yourself than to others,\dots\\~\\

\centering\uncover<2->{\alert{``I deserve to be here.''}}

\end{frame}

\begin{frame}
\frametitle{We need consistent attitude adjustments.}
Seven of the nine beatitudes focus on the condition of our heart.\\~\\
\begin{quote}
For the word of God is living and active, sharper than any two-edged sword, piercing to the division of soul and of spirit, of joints and of marrow, and \textbf{discerning the thoughts and intentions of the heart}.

\attrib{\bibleverse{Heb}(4:12), ESV}
\end{quote}

\begin{quote}
What I am eager for is that all the Christians there will be filled with \textbf{love that comes from pure hearts},and that their minds will be clean and their faith strong.

\attrib{\bibleverse{ITim}(1:5), TLB}
\end{quote}
\end{frame}

\begin{frame}
\frametitle{This week's readings teach us\\what a good heart looks like.}
Peter says to the Lord,\\``Depart from me for I am a sinful man.''\\~\\
Jesus forgives the sins of a paralytic man.\\~\\
Jesus calls Matthew, a tax collector.
\end{frame}

\begin{frame}
\frametitle{We need a humble heart that recognizes\\our dependence on Jesus.}
\end{frame}

\begin{frame}
\frametitle{Physicians are for the Sick}
\tableofcontents[sectionstyle=show/show]
\end{frame}

\section{We do not deserve to be in the presence of Jesus.}
\begin{frame}
\frametitle{A miraculous catch of fish}
\end{frame}

\begin{frame}
\frametitle{}
\end{frame}

\section{But, Jesus is the only one with power to forgive us.}
\begin{frame}
\frametitle{Jesus cures a paralytic}
\end{frame}

\section{So, He comes to us, when we could not come to Him.}
\begin{frame}
\frametitle{}
\end{frame}

\section*{Conclusion}
\begin{frame}
\frametitle{Know who you are.}
A sinner,~~~~~forgiven.
\end{frame}
\end{document}
